Dominance Regions for Rank Two Cluster Algebras

### 2022-04-07 dominance_regions.tex
More superscripts

  The recursion can be written more succinctly as $u_{i+1,\varepsilon}=u_{2,\varepsilon}u_{i,-\varepsilon}-u_{i-1,\varepsilon}$ with the additional initial condition $u_{2,\varepsilon}=\begin{cases} b & \text{if $\varepsilon=+$;}\\ c & \text{if $\varepsilon=-$.} \end{cases}$
  This leads to the following more general recursive structure.
  \begin{lemma}
    For $i,\ell\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
    \begin{equation}
      \label{eq:long Chebyshev recursion}
      u_{i+\ell,\varepsilon}=\begin{cases} u_{\ell+1,\varepsilon}u_{i,-\varepsilon}-u_{\ell,-\varepsilon}u_{i-1,\varepsilon} & \text{\upshape if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i,\varepsilon}-u_{\ell,\varepsilon}u_{i-1,-\varepsilon} & \text{\upshape if $\ell$ is even.} \end{cases}
    \end{equation}
    \begin{equation}
      \label{eq:long Chebyshev recursion}
      u_{i+\ell}^\varepsilon=\begin{cases} u_{\ell+1}^\varepsilon u_i^{-\varepsilon}-u_\ell^{-\varepsilon} u_{i-1}^\varepsilon & \text{\upshape if $\ell$ is odd;}\\ u_{\ell+1}^{-\varepsilon} u_i^\varepsilon-u_\ell^\varepsilon u_{i-1}^{-\varepsilon} & \text{\upshape if $\ell$ is even.} \end{cases}
    \end{equation}
  \end{lemma}
  \begin{proof}
    We work by induction on $\ell$, the cases $\ell=0,1$ being tautological and reproducing the defining recursion, respectively.
    Using the claim for $\ell>0$ and then the defining recursion twice, we get
    \begin{align*}
      u_{i+\ell+1,\varepsilon}&=\begin{cases} u_{\ell+1,\varepsilon}u_{i+1,-\varepsilon}-u_{\ell,-\varepsilon}u_{i,\varepsilon} & \text{if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i+1,\varepsilon}-u_{\ell,\varepsilon}u_{i,-\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
      &=\begin{cases} (u_{2,-\varepsilon}u_{\ell+1,\varepsilon}-u_{\ell,-\varepsilon})u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell$ is odd;}\\ (u_{2,\varepsilon}u_{\ell+1,-\varepsilon}-u_{\ell,\varepsilon})u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
      &=\begin{cases} u_{\ell+2,-\varepsilon}u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell+1$ is even;}\\ u_{\ell+2,\varepsilon}u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell+1$ is odd;} \end{cases}
    \end{align*}
    which is the claimed recursion for $\ell+1$.
    These calculations can be reversed to show the result for $\ell<0$.
  \end{proof}

>>>>

  The recursion can be written more succinctly as $u_{i+1}^\varepsilon=u_2^\varepsilon u_i^{-\varepsilon}-u_{i-1}^\varepsilon$ with the additional initial condition $u_2^\varepsilon=\begin{cases} b & \text{if $\varepsilon=+$;}\\ c & \text{if $\varepsilon=-$.} \end{cases}$
  This leads to the following more general recursive structure.
  \begin{lemma}
    For $i,\ell\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
    \begin{equation}
      \label{eq:long Chebyshev recursion}
      u_{i+\ell}^\varepsilon=\begin{cases} u_{\ell+1}^\varepsilon u_i^{-\varepsilon}-u_\ell^{-\varepsilon} u_{i-1}^\varepsilon & \text{\upshape if $\ell$ is odd;}\\ u_{\ell+1}^{-\varepsilon} u_i^\varepsilon-u_\ell^\varepsilon u_{i-1}^{-\varepsilon} & \text{\upshape if $\ell$ is even.} \end{cases}
    \end{equation}
  \end{lemma}
  \begin{proof}
    We work by induction on $\ell$, the cases $\ell=0,1$ being tautological and reproducing the defining recursion, respectively.
    Using the claim for $\ell>0$ and then the defining recursion twice, we get
    \begin{align*}
      u_{i+\ell+1}^\varepsilon
      &=
      \begin{cases} 
        u_{\ell+1}^\varepsilon u_{i+1}^{-\varepsilon}-u_\ell^{-\varepsilon} u_i^\varepsilon & \text{if $\ell$ is odd;}\\
        u_{\ell+1}^{-\varepsilon} u_{i+1}^\varepsilon-u_\ell^\varepsilon u_i^{-\varepsilon} & \text{if $\ell$ is even;} 
      \end{cases}\\
      &=
      \begin{cases} 
        (u_2^{-\varepsilon} u_{\ell+1}^\varepsilon-u_\ell^{-\varepsilon}) u_i^\varepsilon-u_{\ell+1}^\varepsilon u_{i-1}^{-\varepsilon} & \text{if $\ell$ is odd;}\\ 
        (u_2^\varepsilon u_{\ell+1}^{-\varepsilon}-u_\ell^\varepsilon) u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon & \text{if $\ell$ is even;}
      \end{cases}\\
      &=
      \begin{cases}
        u_{\ell+2}^{-\varepsilon} u_i^\varepsilon - u_{\ell+1}^\varepsilon u_{i-1}^{-\varepsilon} & \text{if $\ell+1$ is even;}\\ 
        u_{\ell+2}^\varepsilon u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon & \text{if $\ell+1$ is odd;}
      \end{cases}
    \end{align*}
    which is the claimed recursion for $\ell+1$.
    These calculations can be reversed to show the result for $\ell<0$.
  \end{proof}
